A Spatial AR System for Axis-aligned Metric Augmentation of Planar Scenes

### 2021-07-17 paper/elsarticle/elsarticle-template.tex
paper

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}\corref{mycorrespondingauthor}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{michael.hornacek@tuwien.ac.at}
\author{Hans K\"{u}ffner-McCauley}
\author{Majesa Trimmel}
\author{Patrick Rupprecht}
\author{Sebastian Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Wien, Vienna, Austria}

@@

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to partake in the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. In turn, \textit{spatial} AR\cite{bimber2019spatial} is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with a head-mounted display, but by projection to the scene itself, thus eliminating both aforementioned problems. Yet considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular; more generally, they will instead appear trapezoidal (i.e., the projected image will appear distorted). Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.

@@

One way to compute a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface. The keystone correction approach of Sukthankar \etal \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Calibrated approach: \cite{raskar2001self}...

@@

...

@@

We recover the scene plane via spatial resection by applying a PnP algorithm \cite{terzakis2020consistently} to the 2D-3D correspondences obtained using a chessboard pattern. Note that this step is separate from camera calibration, yet could well be carried out using the same calibration pattern used in the camera calibration step.\footnote{The critical point is that the pattern should ideally be coplanar with the local scene plane, meaning its height above the scene plane should not exceed a few millimeters.} While a single image of such a chessboard pattern placed on the floor could be sufficient if the floor is even, we place a chessboard pattern in close proximity to the projected circles pattern in each projector calibration image in order to recover the scene plane locally to each target location, in order to account for the possibility of an uneven floor. Note that in principle, we could project a chessboard pattern instead of a circles pattern to obtain the 2D-3D correspondences needed for projector calibration; it is, however, because we rely on detecting the corners of a chessboard pattern to recover the scene plane that we opt instead for a alternative pattern.

@@

We presented a spatial AR system for planar scenes that produces the effect of keystone correction analytically, in a manner that enables intuitive placement the augmentations in accordance with the axes of an image of the scene acquired by a downwards-facing camera and such that the desired dimensions of augmentations can be specified in metric terms. Moreover, we showed our system to be able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view. Our evaluation demonstrated our approach to produce compelling results at less time than the more cumbersome traditional manual approach to keystone correction.

>>>>

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}\corref{mycorrespondingauthor}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{michael.hornacek@tuwien.ac.at}
\author{Hans K\"{u}ffner-McCauley}
\author{Majesa Trimmel}
\author{Patrick Rupprecht}
\author{Sebastian~Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Wien, Vienna, Austria}

@@

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to partake in the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. In turn, \textit{spatial} AR\cite{bimber2019spatial} is a form of augmented reality carried out not by embedding the augmentation in an image of the scene as with a head-mounted display, but by projection to the scene itself, thus eliminating both aforementioned problems. Yet considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular. Such distortions can be eliminated by carrying out a cumbersome manual process called keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.

@@

One way to compute a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface. The keystone correction approach of Sukthankar \etal \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Tilt sensors can be used to recover the projector's gravity vector, and be integrated in the computation of a homography as in Raskar and Beardsley \cite{raskar2001self}.

@@

@@

We recover the scene plane via spatial resection by applying a PnP algorithm \cite{collins2014infinitesimal} to the 2D-3D correspondences obtained using a chessboard pattern. Note that this step is separate from camera calibration, yet could well be carried out using the same calibration pattern used in the camera calibration step.\footnote{The critical point is that the pattern should ideally be coplanar with the local scene plane, meaning its height above the scene plane should not exceed a few millimeters.} While a single image of such a chessboard pattern placed on the floor could be sufficient if the floor is even, we place a chessboard pattern in close proximity to the projected circles pattern in each projector calibration image in order to recover the scene plane locally to each target location, in order to account for the possibility of an uneven floor. Note that in principle, we could project a chessboard pattern instead of a circles pattern to obtain the 2D-3D correspondences needed for projector calibration; it is, however, because we rely on detecting the corners of a chessboard pattern to recover the scene plane that we opt instead for a alternative pattern.

@@

We presented a spatial AR system for planar scenes that produces the effect of keystone correction analytically, in a manner that enables intuitive placement the augmentations in accordance with the axes of an image of the scene acquired by a downwards-facing camera, and such that the desired dimensions of augmentations can be specified in metric terms. Moreover, we showed our system to be able to handle a projector equipped with a steerable mirror, enabling factory floor augmentation exceeding the bounds of the projector's own immediate field of view. Our evaluation demonstrated our approach to produce compelling results at less time than the more cumbersome traditional manual approach to keystone correction.
